Project Protocol

### 2019-10-18 protocol.Rmd
aims

1. Show that spatial disease trends, that impact highly populated small areas, are detected with higher accuracy when viewed in a hexagon tile map display.

@@

##	Participants
We will aim to survey 100 participants.
Participants will be approached via their dashboard through their Figure-Eight accounts.

>>>>

1. Are spatial disease trends, that impact highly populated small areas,  detected with higher accuracy when viewed in a hexagon tile map display?
2. Are people faster in detecting spatial disease trends, that impact highly populated small areas, when using a hexagon tile map display?
3. Do people find hexagon tile maps more difficult to read than choropleth maps?
4. Are the reasons for choosing a plot different depending on the type of display?
5. Does an Australian resident find the choropleth map easier to read than the hexagon tile map?

@@

##	Participants
We will aim to survey 100 participants.
It will be advertised to potential participants via their dashboard through their Figure-Eight accounts.
